pdp: An R Package for Creating Partial Dependence Plots

### 2016-09-02 manuscript/greenwell.tex
finished? XGBoost example

To use \code{partial} with the \code{"xgb.Booster"} class, we need to supply the original training data (minus the response!) in the call to \code{partial}. The following snippet of code computes the partial dependence of \code{cmedv} on both \code{rm} and \code{lstat}, individually and together. The results are displayed in Figure~\ref{fig:boston_xgb}.
\begin{example}
partial(boston.xgb, pred.var = "lstat", train = subset(boston, select = -cmedv),
        plot = TRUE)
\end{example}

>>>>

To use \code{partial} with the \code{"xgb.Booster"} class, we need to supply the original training data (minus the response!) in the call to \code{partial}. The following snippet of code computes the partial dependence of \code{cmedv} on both \code{rm} and \code{lstat}, individually and together. The results are displayed in Figure~\ref{fig:boston_xgb}. Note that while \code{xgboost} requires the training data to be a matrix (or an object of class \code{"dgCMatrix"} or \code{"xgb.DMatrix"}), \code{partial} requires the training data as a data frame with factors in tact!
\begin{example}
pred.list <- list("lstat", "rm", c("lstat", "rm"))
for (x in pred.list) {
  partial(boston.xgb, pred.var = x, train = subset(boston, select = -cmedv),
          plot = TRUE)
}
\end{example}
